Standalone Tactics using OpenTheory

### 2012-02-13 paper.tex
tweak a couple of sentences in intro

We contend that proof tools for interactive theorem provers need only be written and maintained in one place rather than once per system, using \emph{standalone tactics} that are available on the internet and use \OpenTheory to communicate.
An added advantage when the tactic is an integration of an external tool is that a user of the interactive theorem prover need not also have installed the external tool, because the standalone tactic can be accessed from a web server where the tool is installed.

>>>>

We contend that proof tools for interactive theorem provers need only be written and maintained in one place rather than once per system, using \emph{standalone tactics} that are available online and communicate using \OpenTheory.
An added advantage when the tactic is an integration of an external tool is that a user of the interactive theorem prover need not install the external tool: it only needs to be available on the server hosting the standalone tactic.
